---
title: "gamedevmverse"
output: html_document
date: "2026-10-01"
---

```{r}

library(multiverse)
library(dplyr)
library(tidyverse)
library(lmerTest)
library(ggplot2)
library(tidyr)
library(broom)
library(lme4)




```
Document for starting out with the multiverse package 

Terminology
- Parameter --> represents a node in the three that has more than one child - so this is the point of decision, not the node itself 
- Option --> is one of the chosen children --> so the node 

practice


```{r}
data("hurricane")

hurricane_data = hurricane |> 
  rename(
    year = Year, 
    name = Name, 
    dam = NDAM, 
    death = alldeaths, 
    female = Gender_MF, 
    category = Category, 
    pressure = Minpressure_Updated_2014, 
    wind = HighestWindSpeed
  ) |> 
  mutate(
        post = ifelse(year>1979, 1, 0),
        zcat = as.numeric(scale(category)),
        zpressure = -scale(pressure),
        zwind = as.numeric(scale(wind)),
        z3 = as.numeric((zpressure + zcat + zwind) / 3)
    )

df.filtered = hurricane_data |> 
  filter(name != "Katrina" & name != "Audrey") |>
  mutate(zpressure = -scale(pressure))

fit = glm(
  death ~ MasFem * dam + MasFem * zpressure,
  data = df.filtered,
  family = "poisson"
  
)

summary(fit)

tidy(fit) |>
  filter(term != "(Intercept)") |>
  ggplot() +
  geom_vline(xintercept = 0, color = "red") +
  geom_pointrange(aes(x = estimate, y = term, xmin = estimate + qnorm(0.025)*std.error, xmax = estimate + qnorm(0.975)*std.error)) +
  theme_minimal()

?geom_point
```
How to transform this single pipe analysis to a multiverse? 


```{r}

M = multiverse()


```

# By this step we are essentially creating an environment for the multiverse analysis to run - this is a necessary feature in a multiverse 



It is necessary to write everything in a multiverse code_chunk, that can be implemented as an addin
#The branch function: 1. the first part defines the parameter 2. the second section determines the options 
```{multiverse default-m-1, inside = M}

df.filtered = df |> 
  filter(branch(death_otuliers, 
                "no_exclusion" ~ TRUE,
                "most_extreme" ~ name != "Katrina", 
                "two_most_extreme" ~ !(name %in% c("Katrina", "Audrey"))
                ))


#There are a bunch of diagnostic functions to evaluate certain properties of the multiverse

code(M)
parameters(M)
conditions(M)
extract_variables(M, df.filtered)
M
```


Here we are defining additional steps in the analysis 

The subsequent multiverse code blocks will be subsequent decisions --> order matters

Logic of parameter definition --> one starts defining the operation in R (e.g. filter, mutate, what not --> and within the operation, the parameter can be added at the specification stage of the operation)

```{multiverse variable definitions, inside = M}

df.filtered = df.filtered |> 
  mutate(femininity = branch(femininity_calculation, 
                             "masfem" ~ MasFem, 
                             "female" ~ female), 
         damage = branch(damage_transform, 
                         "no_log_transform" ~ identity(dam), 
                         "log_transform" ~ log(dam)))



parameters(M)
```


Implementing models in the multiverse 
 
 This does not only apply to models, but for other decisions of this nature too 
 - Certain branches could be reused if subsequent choices "belong together" --> e.g. Poisson model only works for certain dvs
 
 with this feature, conceptual decisions that have impacts in multiple stages of the analysis can be defnied together 
 - Extremely useful for our case
 

```{multiverse default-m-3, inside = M}

  fit = glm(branch(mod_type, 
         "linear" ~ log(death + 1), 
         "poisson" ~ death) 
  ~ femininity * dam + femininity * zpressure,
  family = branch(mod_type, "linear" ~ gaussian, 
                            "poisson" ~ poisson), data = df.filtered)
```

It is possible to introduce conditional options at certain parameters --> with the %when% operator right after the option 



```{multiverse default-m-4, inside = M}

fit = glm(death ~ branch(main_interaction, "no" ~ femininity + dam, 
                         "yes" ~ femininity * dam) + 
                  branch(other_predictors,
                         "None" ~ NULL, 
                         "pressure" %when% (main_interaction == "yes") ~ femininity * zpressure, 
                         "wind" %when% (main_interaction == "yes") ~ femininity * zwind,
                         "category" %when% (main_interaction == "yes") ~ femininity * zcat,
                         "all" %when% (main_interaction == "yes") ~ femininity * z3,
                         "all_no_interaction" %when% (main_interaction == "no") ~ z3),
                          family = "poisson", data = df.filtered)
                                                            

```


You can extract results of individual pipes but that will become important later


Executing the entire multiverse

```{multiverse default-m-5, inside = M}
execute_multiverse(M, parallel = TRUE, progress = TRUE)


?progress


```